Post-replication citation patterns in psychology: Four case studies

### 2021-02-06 manuscript/manuscript.Rmd
added discussion section

The study protocol (rationale, methods, and analysis plan) was pre-registered on April 7th 2018 (https://osf.io/eh5qd/). An amended protocol was registered part way through data collection on May 1st 2019, primarily because we extended the sampling frame to cover additional months (https://osf.io/pdvb5/). All deviations from these protocols are explicitly acknowledged in Supplementary Information \@ref(appA). All data exclusions and measures conducted during this study are reported.

@@

### Qualitative assessment
Qualitative assessment of citation patterns was limited to a time period starting one year prior to the year of publication of the replication study up until 31st December, 2019, excluding the year in which the replication was published. We excluded the replication year because it may be unreasonable to expect citing articles already in the publication pipeline to cite the replication study. For the Baumeister case, the qualitative analysis was based on a random sample of 40% of citing articles from the pre-replication period and post-replication period due to the large number of citations to the original study (n = `r d_citations %>% filter(case=='baumeister') %>% nrow()`; see Supplementary Information \@ref(appB) for details).

@@

Figure \@ref(fig:citeCurves) shows standardized annual citation counts for each original study and the respective reference class (citations to all articles published in the same year and same journal as the original study), and classifications of citation valence (favourable, equivocal, unfavourable, unclassifiable or excluded). The data can also be viewed in tabular format in Supplementary Table \@ref(tab:tabularData). All counts (n) reported in the text and table are raw counts (i.e., not standardized).

@@

Figure \@ref(fig:repPlot) shows the proportion of citing articles that also cited or did not cite the replication study after it was published (excluding the publication year itself). The data can also be viewed in tabular format in Supplementary Table \@ref(tab:tabularData). In the Strack and Baumeister cases, a considerable majority of articles citing the original study did not cite the replication study, indicating substantial citation bias. In the Baumeister case the proportion of articles citing the replication study remained stable (`r round(citesRep_Bau2017,2)*100`% in 2017, `r round(citesRep_Bau2019,2)*100`% in 2019). In the Strack case, the proportion increased from `r round(citesRep_Strack2017,2)*100`% to `r round(citesRep_Strack2019,2)*100`%. In the Carter and Caruso cases, the proportion never exceeded `r round(citesRep_carter_caruso_max,2)*100`%, also consistent with substantial citation bias. In the Sripada case, it was much more common for the replication study to be cited (>`r round(citesRep_sripada,2)*100`%) reflecting a balanced citation pattern.

@@

In additional exploratory analyses (not pre-registered) we examined other characteristics of the ` d_contentAnalysis %>% filter(citesReplication==T,counterArguments==T) %>% distinct(doi) %>% nrow()` unique articles that contained counter-arguments. The articles were published in `r nrow(ca_journals)` individual journals, with *Frontiers in Psychology* publishing `r ca_journals %>% filter(journal == 'FRONTIERS IN PSYCHOLOGY') %>% pull(n)` of the articles, *Social Psychology* publishing `r ca_journals %>% filter(journal == 'SOCIAL PSYCHOLOGY') %>% pull(n)` of the articles, and all other journals publishing only 1 or 2 of the articles. `r ca_noData` of the articles did not involve empirical data, `r ca_existData` involved reanalysis or meta-analysis of existing data, and `r ca_novData` involved collection of novel data. The articles had `r nrow(ca_auth_freq)` individual authors of whom all contributed to a single article except for `r ca_auth_freq %>% filter(Freq > 1) %>% nrow()` individuals who had (co)authored 2 articles. `r org_auths_overlap` articles were (co)authored by one of the original authors and `r co_auths_overlap` articles were (co)authored by at least one prior collaborator of one of the first authors of the original articles. `r overlapArtTypes %>% filter(articleType == "No empirical data") %>% pull(n)` of these articles did not involve empirical data and `r overlapArtTypes %>% filter(articleType != "No empirical data") %>% pull(n) %>% sum()` of them involved novel data collection.

# Discussion

# Open practices statement

The study protocol (hypotheses, methods, and analysis plan) was pre-registered on April 7th 2018 (https://osf.io/eh5qd/). An amended protocol was registered on May 1st 2019 (https://osf.io/pdvb5/). All deviations from these protocol or additional exploratory analyses are explicitly acknowledged. All data exclusions and measures conducted during this study are reported. All data, materials, and analysis scripts related to this study are publicly available on The Open Science Framework (https://osf.io/w8h2q/). To facilitate reproducibility this manuscript was written by interleaving regular prose and analysis code (TBA) using knitr [@Xie:2018aa] and papaja [@R-papaja], and is available in a Code Ocean container (TBA) which re-creates the software environment in which the original analyses were performed,

# Funding statement

# Conflict of interest statement

The authors declare no conflicts of interest.

# Author contributions:

@@

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in

>>>>

The study protocol (rationale, methods, and analysis plan) was pre-registered on April 7th 2018 (https://osf.io/eh5qd/). An amended protocol was registered part way through data collection on May 1st 2019, primarily because we extended the sampling frame to cover additional months (https://osf.io/pdvb5/). All deviations from these protocols are explicitly acknowledged in Appendix \@ref(appA). All data exclusions and measures conducted during this study are reported.

@@

### Qualitative assessment
Qualitative assessment of citation patterns was limited to a time period starting one year prior to the year of publication of the replication study up until 31st December, 2019, excluding the year in which the replication was published. We excluded the replication year because it may be unreasonable to expect citing articles already in the publication pipeline to cite the replication study. For the Baumeister case, the qualitative analysis was based on a random sample of 40% of citing articles from the pre-replication period and post-replication period due to the large number of citations to the original study (n = `r d_citations %>% filter(case=='baumeister') %>% nrow()`; see Appendix \@ref(appB) for details).

@@

Figure \@ref(fig:citeCurves) shows standardized annual citation counts for each original study and the respective reference class (citations to all articles published in the same year and same journal as the original study), and classifications of citation valence (favourable, equivocal, unfavourable, unclassifiable or excluded). The data can also be viewed in tabular format in Appendix \@ref(tab:tabularData). All counts (n) reported in the text and table are raw counts (i.e., not standardized).

@@

Figure \@ref(fig:repPlot) shows the proportion of citing articles that also cited or did not cite the replication study after it was published (excluding the publication year itself). The data can also be viewed in tabular format in Appendix \@ref(tab:tabularData). In the Strack and Baumeister cases, a considerable majority of articles citing the original study did not cite the replication study, indicating substantial citation bias. In the Baumeister case the proportion of articles citing the replication study remained stable (`r round(citesRep_Bau2017,2)*100`% in 2017, `r round(citesRep_Bau2019,2)*100`% in 2019). In the Strack case, the proportion increased from `r round(citesRep_Strack2017,2)*100`% to `r round(citesRep_Strack2019,2)*100`%. In the Carter and Caruso cases, the proportion never exceeded `r round(citesRep_carter_caruso_max,2)*100`%, also consistent with substantial citation bias. In the Sripada case, it was much more common for the replication study to be cited (>`r round(citesRep_sripada,2)*100`%) reflecting a balanced citation pattern.

@@

In additional exploratory analyses (not pre-registered) we examined other characteristics of the `r d_contentAnalysis %>% filter(citesReplication==T,counterArguments==T) %>% distinct(doi) %>% nrow()` unique articles that contained counter-arguments. The articles were published in `r nrow(ca_journals)` individual journals, with *Frontiers in Psychology* publishing `r ca_journals %>% filter(journal == 'FRONTIERS IN PSYCHOLOGY') %>% pull(n)` of the articles, *Social Psychology* publishing `r ca_journals %>% filter(journal == 'SOCIAL PSYCHOLOGY') %>% pull(n)` of the articles, and all other journals publishing only 1 or 2 of the articles. `r ca_noData` of the articles did not involve empirical data, `r ca_existData` involved reanalysis or meta-analysis of existing data, and `r ca_novData` involved collection of novel data. The articles had `r nrow(ca_auth_freq)` individual authors of whom all contributed to a single article except for `r ca_auth_freq %>% filter(Freq > 1) %>% nrow()` individuals who had (co)authored 2 articles. `r org_auths_overlap` articles were (co)authored by one of the original authors and `r co_auths_overlap` articles were (co)authored by at least one prior collaborator of one of the first authors of the original articles. `r overlapArtTypes %>% filter(articleType == "No empirical data") %>% pull(n)` of these articles did not involve empirical data and `r overlapArtTypes %>% filter(articleType != "No empirical data") %>% pull(n) %>% sum()` of them involved novel data collection.

Discussion
It has been proposed that replication studies can facilitate scientific self-correction by modifying scientists’ belief in the credibility of published findings (Ioannidis, 2012; Vazire & Holcombe, 2020; Zwaan et al., 2018); however, the extent to which this occurs in practice is unclear. In this study, we investigated how the research community responded to four strongly contradictory replications in the field of psychology by examining post-replication citation patterns for original studies. We observed some ‘progressive’ response in the form of modest active correction patterns (a small decline in favourable citations and a small increase in unfavourable citations), but also even more prominent ‘regressive’ responses in the form of unchallenged belief perpetuation (sustained levels of favourable citations and few unfavourable citations, particularly in the Baumeister case) and considerable citation bias (neglecting to cite the replication study; in all cases aside from Sripada). When authors cited the original study favourably despite the replication result, only half of the articles provided any explicit counter arguments in defence of the original study (an explicit defence). Overall, these findings are consistent with prior observations that favourable citation patterns can continue relatively unperturbed by subsequent publication of contradictory results in studies with lower risk of bias (Tatsioni et al., 2007) or even by full retraction (Budd et al., 1998), and that positive (supportive) evidence is preferentially cited relative to negative (non-supportive) evidence once a theory gets entrenched despite overwhelming evidence against it (Greenberg, 2009).

It is reasonable to question whether the replication results in these case studies should (rationally) have instigated belief change in the research community and thus triggered a more sizable decline in favourable citations than we observed. It is important to note that the case studies we selected were deliberately chosen because the replication results were superior to the original results in terms of both credibility and evidential value. The replications were pre-registered, muli-laboratory studies with large sample sizes. By contrast, the original studies had much smaller sample sizes, and arguably had a much higher risk of bias, as they were not pre-registered, were performed by single teams, and arose in domains affected by publication bias and other questionable research practices (E. C. Carter et al., 2015; Coles et al., 2019; Vadillo, 2019; Vadillo et al., 2016). Thus, it seems reasonable to suggest that the compelling replication results should have reduced belief in the credibility of the original results.

The clear evidence of citation bias that our study documents may have two main contributory factors: (1) a lack of awareness about the replication results; and/or (2) a decision to ignore the replication results. The practical issue of awareness is not necessarily straightforward to address. Individual scientists can find it difficult to keep up-to-date with the voluminous literature that is relevant to their research. Recently, the reference manager Zotero has introduced a feature that alerts users when an article in their database has been retracted (Zotero, 2019). One could imagine a similar feature being introduced for replication studies, perhaps based on databases that explicitly identify replication studies such as Curate Science (https://curatescience.org/). However, it is much less straightforward to define a relevant replication study (Neuliep & Crandall, 1993) and users would need to be alerted that this requires some scientific judgement rather than simple article meta-data. Another solution could be to encourage researchers to focus less on individual studies and more on up-to-date evidence summaries (i.e., reviews and meta-analyses) in which relevant evidence is systematically identified and collated. This would require that high-quality and contemporary evidence summaries are available; however, in psychology systematic reviews and meta-analyses can be of low quality and their results may still be inflated and irreproducible (Kvarven et al., 2020; Maassen et al., 2020; Polanin et al., 2020). Moreover, most empirical studies are not included in any form of evidence synthesis (Hardwicke et al., 2020).

The second issue of authors ignoring highly relevant replications is undesirable and implies a biased appraisal of the evidence. Contradictory replication results do not necessarily nullify the credibility of an original study (Collins, 1985; Earp & Trafimow, 2015; Maxwell et al., 2015), but we would still expect highly relevant replication results to be cited and explicitly debated. In fact, we found that when authors continued to favourably cite original studies despite the replication results, around half did not provide explicit counter-arguments in defence of the original study. Although our study did not examine researchers’ individual beliefs, one recent study found that when research psychologists were confronted with replication evidence, they often did update their (self-reported) beliefs, albeit modestly (McDiarmid et al., 2021). However, there are several reasons to be uncertain about whether the results from this artificial setting might generalize to real-world settings, including potential observer bias (i.e., participants behaving differently because they are under observation and/or responding to the perceived expectations of the research team) and the possibility that individuals may behave differently in settings where they have substantial personal investment and may be publicly scrutinized. Additionally, cognitive psychology studies have obtained some evidence of a ‘continued influence effect’ wherein an individual's beliefs and behaviour can continue to be influenced by false or misleading information despite subsequent efforts to reject it (Lewandowsky et al., 2012). It is plausible that various cognitive biases, such as confirmation bias (preferentially seeking out and processing evidence that supports pre-existing beliefs) or motivated reasoning (constructing and evaluating arguments based on what is desirable rather than what is rationally justifiable), may partly explain researchers' tendency to ignore or dismiss the replication evidence (Bishop, 2019; Kunda, 1990; Nickerson, 1998).

We observed that when counter-arguments were raised, most of them tried to dismiss the contradictory replication by claiming that the original and the replication studies differed in important ways that moderated the absence/presence of the effect under investigation. In some cases, authors pointed to evidence from other studies as a rationale for their continued belief in the effect. In a minority of cases, the authors challenged the competence of replicators. We found that articles presenting counter-arguments were published in a variety of journals (rather than clustered in a few journals), and involved collection of new data in around half of the cases. They were also published by a sizeable group of investigators, only a minority of whom were one of the original authors or had previously collaborated with one of the original first authors. This suggests that the explicit defence of the original study came from a variety of sources rather than being confined to a small number of investigators. However, note that this analysis may underestimate authorship overlap due to difficulties isolating individual researcher identities (see methods section) and articles published in the same year as the replication were not included.

The findings presented here are inherently limited by the observational nature of the study design, which complicates straightforward conclusions about the causal impact of the replications. Although the use of a reference class enables us to detect the influence of exogenous factors to some extent, we cannot rule out their contribution. For example, the modest decline in favourable citations observed in most cases could be attributable, at least in part, to a more general awareness in the research community about methodological issues (for example, that the sample sizes of the original studies may not have provided sufficient statistical power). We have also focused only on the replication study and the original study in each case study, without considering the impact of other potentially relevant events. Notably, meta-research studies have detected signatures of publication bias and other questionable research practices in the fields to which these case studies belong (E. C. Carter et al., 2015; Coles et al., 2019; Vadillo, 2019; Vadillo et al., 2016) and other relevant replication studies contesting prior findings have been published (e.g., Rohrer et al., 2015).

We have only been able to gauge reactions to replications to the extent that they are reflected in citation patterns. Thus, for example, our method would not detect if there had been a self-correction effect amongst individuals who would not typically cite the original study, such as students, members of the public, or researchers working in other fields. A contested study may continue to be  cited favourably by its proponents who remain working in the field. This will suffice to create belief perpetuation in the published literature, even though other scientists may simply no longer be interested in getting involved with such a strongly contested research topic. Relatedly, we did not examine citation patterns beyond 3-5 years post-replication. Some perspectives envision scientific self-correction unfolding over a much longer time scale (Lauden, 1981; Peterson & Panofsky, 2020) and suggest the process is characterised less by the impact of individual study results and more by the gradual accumulation of converging evidence, gradual revision of theoretical understanding, and/or informal sociological processes (e.g., researchers choosing alternative topics to study). Thus, whilst the current findings may contradict the expectations of a more direct and expedited view of the corrective impact of replication studies (Ioannidis, 2012; Vazire & Holcombe, 2020), they are not necessarily inconsistent with a slower and more indirect process of self-correction.

Generalization beyond these four case studies requires caution. Of note, the replication studies examined here were some of the first large-scale multi-laboratory replication attempts conducted in the field of psychology. This gave them particular prominence and initiated considerable debate, resulting in broader ramifications beyond the research community that typically studies the topics under scrutiny (Nelson et al., 2018). Also of note, we deliberately selected case studies where the replication studies were high-profile and had yielded high credibility evidence that strongly contradicted and outweighed the original findings. A self-correction effect may be less expected in cases where replication results are more ambiguous, less consequential, or less well-known. For example, in a situation where two high credibility studies with similar evidential value yield contradictory results, it would be premature to lose confidence in one of the studies before further investigation has probed the cause of the discrepancy. Pursuit of potential moderating factors may be entirely rational in such circumstances (Gershman, 2019).

We should also highlight that particular aspects of our study were inherently subjective, specifically, the identification of citation context, the classification of citation valence, and the identification, extraction, and categorisation of counter-arguments. In order to minimize subjectivity, a team of six investigators performed all coding in duplicate, with a third investigator arbitrating if necessary. As disagreements between primary and secondary coders were infrequent, we are confident that the classifications are meaningful, but there may be some edge cases when an independent observer might reasonably disagree with our classifications.

In conclusion, post-replication citation patterns in four case studies indicated that the anticipated corrective impact of strongly contradictory replication results did not materialise to any substantive degree. A lack of awareness of replications and/or a decision to discount them appears to have played a significant role. This highlights potential practical problems with the discoverability of replication studies and psychological or sociological issues related to belief change. The findings also indicate that scientific self-correction may not be as expedient or straightforward as one might hope (Ioannidis, 2012), adding further impetus towards efforts to improve the quality of the academic literature (Hardwicke et al., 2020; Nelson et al., 2018).

# Materials, data, and analysis code availability
All data, materials, and analysis scripts related to this study are publicly available on the Open Science Framework (https://osf.io/w8h2q/). To facilitate reproducibility this manuscript was written by interleaving regular prose and analysis code using knitr (Xie, 2017) and papaja (Aust & Barth, 2020), and is available in a Code Ocean container (TO BE ADDED) which re-creates the software environment in which the original analyses were performed.

# Funding statement
The authors received no specific funding for this work. The Meta-Research Innovation Center at Stanford (METRICS) is supported by a grant from the Laura and John Arnold Foundation. The Meta-Research Innovation Center Berlin (METRIC-B) is supported by a grant from the Einstein Foundation and Stiftung Charité. The work of John Ioannidis is supported by an unrestricted grant from Sue and Bob O’Donnell. Robert T. Thibault is supported by a postdoctoral fellowship from the Fonds de la recherche en santé du Québec. Tom E. Hardwicke receives funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No. 841188. Denes Szucs receives funding from the James S. McDonnell Foundation 21st Century Science Initiative in Understanding Human Cognition (grant number 220020370). Olmo R. van den Akker is supported by a Consolidator Grant (IMPROVE) from the European Research Council (ERC; grant no. 726361).

# Conflict of interest statement
The authors declare no conflicts of interest.

# Author contributions
TEH, DS, and JPAI designed the study. TEH, DS, RTT, SC, ORA, and MN performed the data extraction and coding. TEH and SC performed the data analysis. TEH wrote the manuscript. All authors provided feedback and approved the manuscript.

Aust, F., & Barth, M. (2020). Papaja: Create apa manuscripts with rmarkdown. https://github.com/crsh/papaja

Bastiaansen, J. A., de Vries, Y. A., & Munafò, M. R. (2015). Citation distortions in the literature on the serotonin-transporter-linked polymorphic region and amygdala activation. Biological Psychiatry, 78(8), E35–E36. https://doi.org/10.1016/j.biopsych.2014.12.007

Baumeister, R. E., Bratslavsky, E., Muraven, M., & Tice, D. M. (1998). Ego depletion: Is the active self a limited resource? Journal of Personality and Social Psychology, 74(5), 1252–1265. https://doi.org/10.1037/0022-3514.74.5.1252

Bishop, D. V. (2019). The psychology of experimental psychologists: Overcoming cognitive constraints to improve research: The 47th Sir Frederic Bartlett Lecture: Quarterly Journal of Experimental Psychology, 73(1), 1–19. https://doi.org/10.1177/1747021819886519

Budd, J. M., Sievert, M., & Schultz, T. R. (1998). Phenomena of retraction: Reasons for retraction and citations to the publications. JAMA, 280(3), 296–297. https://doi.org/10.1001/jama.280.3.296

Carter, E. C., Kofler, L. M., Forster, D. E., & McCullough, M. E. (2015). A series of meta-analytic tests of the depletion effect: Self-control does not seem to rely on a limited resource. Journal of Experimental Psychology. General, 144(4), 796–815. https://doi.org/10.1037/xge0000083

Carter, T. J., Ferguson, M. J., & Hassin, R. R. (2011). A single exposure to the american flag shifts support toward republicanism up to 8 months later. Psychological Science, 22(8), 1011–1018. https://doi.org/10.1177/0956797611414726

Caruso, E. M., Vohs, K. D., Baxter, B., & Waytz, A. (2013). Mere exposure to money increases endorsement of free-market systems and social inequality. Journal of Experimental Psychology: General, 142(2), 301–306. https://doi.org/10.1037/a0029288

Coles, N. A., Larsen, J. T., & Lench, H. C. (2019). A meta-analysis of the facial feedback literature: Effects of facial feedback on emotional experience are small and variable. Psychological Bulletin, 145(6), 610–651. https://doi.org/10.1037/bul0000194

Collins, H. M. (1985). Changing order: Replication and induction in scientific practice. Sage Publications.

Earp, B. D., & Trafimow, D. (2015). Replication, falsification, and the crisis of confidence in social psychology. Frontiers in Psychology, 6, 621. https://doi.org/10.3389/fpsyg.2015.00621

Etz, A., & Vandekerckhove, J. (2016). A Bayesian perspective on the Reproducibility Project: Psychology. PLOS ONE, 11(2), e0149794. https://doi.org/10.1371/journal.pone.0149794

Gershman, S. J. (2019). How to never be wrong. Psychonomic Bulletin & Review, 26(1), 13–28. https://doi.org/10.3758/s13423-018-1488-8

Greenberg, S. A. (2009). How citation distortions create unfounded authority: Analysis of a citation network. BMJ, 339. https://doi.org/10.1136/bmj.b2680

Hagger, M. S., Chatzisarantis, N. L. D., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., Brand, R., Brandt, M. J., Brewer, G., Bruyneel, S., Calvillo, D. P., 
Campbell, W. K., Cannon, P. R., Carlucci, M., Carruth, N. P., Cheung, T., Crowell, A., De Ridder, D. T. D., Dewitte, S., … Zwienenberg, M. (2016). A multilab preregistered replication of the ego-depletion effect. Perspectives on Psychological Science, 11(4), 546–573. https://doi.org/10.1177/1745691616652873

Hardwicke, T. E., Serghiou, S., Janiaud, P., Danchev, V., Crüwell, S., Goodman, S. N., & Ioannidis, J. P. A. (2020). Calibrating the Scientific Ecosystem Through Meta-Research. Annual Review of Statistics and Its Application, 7(1), 11–37. https://doi.org/10.1146/annurev-statistics-031219-041104

Hardwicke, T. E., Thibault, R. T., Kosie, J., Wallach, J. D., Kidwell, M. C., & Ioannidis, J. (2021). Estimating the prevalence of transparency and reproducibility-related research practices in psychology (2014-2017). Perspectives on Psychological Science. https://doi.org/10.31222/osf.io/9sz2y

Ioannidis, J. P. A. (2012). Why science is not necessarily self-correcting. Perspectives on Psychological Science, 7(6), 645–654. https://doi.org/10.1177/1745691612464056

Klein, R. A., Ratliff, K. A., Vianello, M., Adams, R. B., Bahník, Š., Bernstein, M. J., Bocian, K., Brandt, M. J., Brooks, B., Brumbaugh, C. C., Cemalcilar, Z., Chandler, J., Cheong, W., Davis, W. E., Devos, T., Eisner, M., Frankowska, N., Furrow, D., Galliani, E. M., … Nosek, B. A. (2014). Investigating variation in replicability. Social Psychology, 45(3), 142–152. https://doi.org/10.1027/1864-9335/a000178

Kühl, T., & Bertrams, A. (2019). Is learning with elaborative interrogation less desirable when learners are depleted? Frontiers in Psychology, 10, 707. https://doi.org/10.3389/fpsyg.2019.00707

Kunda, Z. (1990). The case for motivated reasoning. Psychological Bulletin, 108(3), 480–498. https://doi.org/10.1037/0033-2909.108.3.480

Kvarven, A., Strømland, E., & Johannesson, M. (2020). Comparing meta-analyses and preregistered multiple-laboratory replication projects. Nature Human Behaviour, 4(4), 423–434. https://doi.org/10.1038/s41562-019-0787-z

Lakatos, I. (1970). Falsification and the methodology of scientific research programmes. In A. Musgrave & I. Lakatos (Eds.), Criticism and the Growth of Knowledge (Vol. 4, pp. 91–196). Cambridge University Press. https://doi.org/10.1017/CBO9781139171434.009

Lauden, L. (1981). Peirce and the trivialization of the self-corrective thesis. In Science and Hypothesis (pp. 226–251). Springer.

Lewandowsky, S., Ecker, U. K. H., Seifert, C. M., Schwarz, N., & Cook, J. (2012). Misinformation and its correction: Continued influence and successful debiasing. Psychological Science in the Public Interest, 13(3), 106–131. https://doi.org/10.1177/1529100612451018

Maassen, E., van Assen, M. A. L. M., Nuijten, M. B., Olsson-Collentine, A., & Wicherts, J. M. (2020). Reproducibility of individual effect sizes in meta-analyses in psychology. PLOS ONE, 15(5), e0233107. https://doi.org/10.1371/journal.pone.0233107

Maxwell, S. E., Lau, M. Y., & Howard, G. S. (2015). Is psychology suffering from a replication crisis? What does “failure to replicate” really mean? American Psychologist, 70(6), 487–498. https://doi.org/10.1037/a0039400

McDiarmid, A., Tullett, A., Whitt, C. M., Vazire, S., Smaldino, P. E., & Stephens, E. E. (2021). Self-correction in psychological science: How do psychologists update their beliefs in response to replications? PsyArXiv. https://doi.org/10.31234/osf.io/hjcm4

Nelson, L. D., Simmons, J., & Simonsohn, U. (2018). Psychology’s Renaissance. Annual Review of Psychology, 69(1), 511–534. https://doi.org/10.1146/annurev-psych-122216-011836

Neuliep, J. W., & Crandall, R. (1993). Everyone was wrong: There are lots of replications out there. Journal of Social Behavior and Personality, 8(6), 1–8.

Nickerson, R. S. (1998). Confirmation Bias: A Ubiquitous Phenomenon in Many Guises. Review of General Psychology, 2(2), 175–220. https://doi.org/10.1037/1089-2680.2.2.175

Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. Science, 349(6251), aac4716–aac4716. https://doi.org/10.1126/science.aac4716

Peterson, D., & Panofsky, A. (2020). Self-correction in science: The diagnostic and integrative motives for replication. SocArXiv. https://doi.org/10.31235/osf.io/96qxv

Polanin, J. R., Hennessy, E. A., & Tsuji, S. (2020). Transparency and reproducibility of meta-analyses in psychology: A meta-review. Perspectives on Psychological Science, 15(4), 1026–1041. https://doi.org/10.1177/1745691620906416

Rohrer, D., Pashler, H., & Harris, C. R. (2015). Do subtle reminders of money change people’s political views? Journal of Experimental Psychology: General, 144(4), e73–e85. https://doi.org/10.1037/xge0000058

Simons, D. J., Holcombe, A. O., & Spellman, B. A. (2014). An introduction to Registered Replication Reports at Perspectives on Psychological Science. Perspectives on Psychological Science, 9(5), 552–555. https://doi.org/10.1177/1745691614543974

Sripada, C., Kessler, D., & Jonides, J. (2014). Methylphenidate blocks effort-induced depletion of regulatory control in healthy volunteers. Psychological Science, 25(6), 1227–1234. https://doi.org/10.1177/0956797614526415

Strack, F. (2017). From data to truth in psychological science. A personal perspective. Frontiers in Psychology, 8, 702. https://doi.org/10.3389/fpsyg.2017.00702

Strack, F., Martin, L. L., & Stepper, S. (1988). Inhibiting and facilitating conditions of the human smile: A nonobtrusive test of the Facial Feedback Hypothesis. Journal of Personality and Social Psychology, 54(5), 768–777. https://doi.org/10.1037/0022-3514.54.5.768

Tatsioni, A., Bonitsis, N. G., & Ioannidis, J. P. A. (2007). Persistence of contradicted claims in the literature. JAMA, 298(21), 2517–2526. https://doi.org/10.1001/jama.298.21.2517

Vadillo, M. A. (2019). Ego depletion may disappear by 2020. Social Psychology, 50(5–6), 282–291. https://doi.org/10.1027/1864-9335/a000375

Vadillo, M. A., Hardwicke, T. E., & Shanks, D. R. (2016). Selection bias, vote counting, and money-priming effects: A comment on Rohrer, Pashler, and Harris (2015) and Vohs (2015). Journal of Experimental Psychology: General, 145(5), 655–663. https://doi.org/10.1037/xge0000157

Vazire, S., & Holcombe, A. O. (2020). Where are the self-correcting mechanisms in science? PsyArXiv. https://doi.org/10.31234/osf.io/kgqzt

Wagenmakers, E.-J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams, R. B., Albohn, D. N., Allard, E. S., Benning, S. D., Blouin-Hudon, E.-M., Bulnes, L. C., Caldwell, T. L., Calin-Jageman, R. J., Capaldi, C. A., Carfagno, N. S., Chasten, K. T., Cleeremans, A., Connell, L., DeCicco, J. M., … Zwaan, R. A. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988). Perspectives on Psychological Science, 11(6), 917–928. https://doi.org/10.1177/1745691616674458

Xie, Y. (2017). Dynamic documents with R and knitr. CRC Press.

Zotero. (2019, June 14). Retracted item notifications with retraction watch integration. https://www.zotero.org/blog/retracted-item-notifications

Zwaan, R. A., Etz, A., Lucas, R. E., & Donnellan, M. B. (2018). Making replication mainstream. Behavioral and Brain Sciences, 41, e120. https://doi.org/10.1017/S0140525X17001972

@@
